SVG: The Paper

### 2022-06-07 Analysis/index.Rmd
figures
updating figure

gather_draws(m, lambda[observer]) %>%
  ggplot(aes(.value, group = observer)) + 
  geom_density(alpha = 0.25, fill = "grey") -> plt_lambdas

(plt_x + plt_y) / plt_lambdas
```

>>>>

gather_draws(m, lambda[observer]) %>%
  median_hdci(.value) %>%
  arrange(.value) %>%
  mutate(observer = factor(observer, levels = observer)) %>%
  ggplot(aes(observer, .value, ymin = .lower, ymax = .upper)) + 
  geom_errorbar() -> plt_lambdas

(plt_x + plt_y) + plt_lambdas

ggsave("../Figures/init_sel2_mdl.pdf", width = 10, height = 5)
```
